Towards a Tool for Verified Hardware Construction

### 2014-06-01 paper.tex
more work on dt section

We can of course

>>>>

We can of course extend our type system with richer features. We will quickly survey the important additions to the Simply
Typed Lambda Calculus that are needed to turn it into a dependently typed lambda calculus. The most important feature
is the idea of Pi Types. Simple type systems can be enriched with many features such as products, sums, so on. There
have been innovations in type system construction, but depdently typed calculi in the style of the CoC or MLTT are
the most powerful.

Traditonally we maintain a phase distinction where types and values leave in seperate universes. Depdent types
are about erasing this distinction. Types can be made more expressive by a series of additions. First if we
allow quantifers we can now abstract over types with type lambdas. We can then introduce kinds which allow us
to specify type arities. We can then introduce kind polymorphism, and many other features. Each of these systems become
more and more complex because they have to maintain constant distinction between each universe of values, kinds, sorts.
Depdent types simply introduce the idea of a Pi Type of dependent function space. This type system generalization is the 
idea that we can make everything much simpler by creating a stratfied hierarchy of types, and combining this Pi Types.
We then can collapse our language into a simple set of pseudo terms, and typing rules \makered{examples can be found}.

The idea of Pi Types can be simply viewed as a generalization of the traditional function type. The generalization
allows the codomain to depdend on the domain of the function. Given $B : P -> A; \Pi (x : A). B(x)$.
